---
title: "data-wrangling 2 practice"
author: "Seonyoung Park (sp3804)"
date: "11/1/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(httr)
```

## Scrap a table

I want the first table from [here]http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm]

read in the html

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)

```

1. extract the table(s); from the website, I've extracted all the tables
2. I'm gonna focus on the first one
3. get html table
4. cut the first row (the “note” at the bottom of the table appears in every column in the first row.)
5. change it to table

```{r}
table_mar = 
  drug_use_html %>%
  html_nodes(css = "table") %>%
  first() %>%
  html_table %>%
  slice(-1) %>%
  as_tibble()

table_mar
```

## Star Wars Movie Info

I want the data from [here](https://www.imdb.com/list/ls070150896/).

```{r}
url="https://www.imdb.com/list/ls070150896/"

swm_html = read_html(url)

```

Grab elements that I want- using SelectorGadget
1. Extract each vector
2. Make a table using all the vectors. 

```{r}
title_vec = 
  swm_html %>%
  html_nodes(css = ".lister-item-header a") %>%
  html_text()

gross_rev_vec = 
  swm_html %>%
  html_nodes(css = ".text-muted .ghost~ .text-muted+ span") %>%
  html_text()

runtime_vec = 
  swm_html %>%
  html_nodes(css = ".runtime") %>%
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    gross_rev = gross_rev_vec,
    runtime = runtime_vec
  )
```

## Get some water data

This is coming from an API; if we can use csv, always use csv first. If not, use Jason, but more work to do. 

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>%
  content("parsed")

nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>%
  jsonlite::fromJSON() %>%
  as_tibble()

```



