---
title: "strings and factors"
author: "Seonyoung Park (sp3804)"
date: "11/1/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(p8105.datasets)
```


## Strings and regex

* str_detect(string, "pattern"); pattern is Case-upper, lower case-specific 
* str_replace(string, "pattern", "new string")

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_replace(string_vec, "jeff", "Jeff")
```

* "^i think" begining of the line
* "i think$" end of the line
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```
* [Aa]: lower or upper case
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )
str_detect(string_vec,"bush")
str_detect(string_vec,"Bush")
str_detect(string_vec,"[Bb]ush")
```
* [0-9][a-zA-Z]: number first followed immediately by letter 
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")

```
* "."; match with literally anything
* 7.11= 7x11 (x can be anything)
* to detect exact 7.11, we have to put "7\\.11"
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
str_detect(string_vec, "7\\.11")
```
* detect open bracket
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")


```

## Factors

* we can see which one is reference (assumed as "1")
```{r}
vec_sex = factor(c("male", "male", "female", "female"))
vec_sex

as.numeric(vec_sex)
```

what happens if I relevel...(switch male into reference)

```{r}
vec_sex = fct_relevel(vec_sex,"male")
vec_sex

as.numeric(vec_sex)

````

## NSDUH - strings

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)


table_mar = 
  read_html(url) %>%
  html_nodes(css = "table") %>%
  first() %>%
  html_table %>%
  slice(-1) %>%
  as_tibble()

table_mar
```

1. Remove P-value column
2. pivot: except for the State column, make pivot
3. age_year; separate age and years by open parenthesis ("\\(")
4. year: remove close parenthesis by replacing with nothing ""
5. percent; remove letter by replacing with nothing "", then change it as numeric. 
6. filter state (not Total U.S. Northeast, Midwest, South, or West)

```{r}
data_mar=
  table_mar %>%
  select(-contains("P value")) %>%
  pivot_longer(
    -State,
    names_to = "age_year",
    values_to =  "percent"
  ) %>%
  separate(age_year, into = c("age", "year"), sep="\\(")%>%
  mutate(
    year = str_replace(year, "\\)", ""),
    percent = str_replace(percent, "[a-c]$", ""),
    percent = as.numeric(percent)
  ) %>% 
  filter(!(State%in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))

data_mar
```


## NSDUH - factors

```{r}
data_mar  %>%
  filter(age=="12-17")

```

Make a plot x=state, y=percent, color = year
* State is character; alphabetical order when plotting

```{r}
data_mar  %>%
  filter(age=="12-17") %>%
  ggplot(aes(State,y=percent,color=year)) +
  geom_point() + theme(axis.text.x=element_text(angle = 90, vjust = 0.5, hjust=1))

```

Let's change State into factor 
1. fct_relevel; with Texas as the very first one. 
2. fct_reorder; in order of percent ranking (from lowest to highest)

```{r}
data_mar  %>%
  filter(age=="12-17") %>%
  mutate(State= fct_relevel(State, "Texas")) %>%
  ggplot(aes(State,y=percent,color=year)) +
  geom_point() + theme(axis.text.x=element_text(angle = 90, vjust = 0.5, hjust=1))

data_mar  %>%
  filter(age=="12-17") %>%
  mutate(State= fct_reorder(State, percent)) %>%
  ggplot(aes(State,y=percent,color=year)) +
  geom_point() + theme(axis.text.x=element_text(angle = 90, vjust = 0.5, hjust=1))


```

