---
title: "strings and factors"
author: "Seonyoung Park (sp3804)"
date: "11/1/2020"
output: github_document
---

```{r setup, include=FALSE}
library(rvest)
library(p8105.datasets)

scale_color_discrete=scale_color_viridis_d
sclae_fill_discrete = scale_fill_viridis_d

```


## Strings and regex

* str_detect(string, "pattern"); pattern is Case-upper, lower case-specific 
* str_replace(string, "pattern", "new string")

```{r}
string_vec = c("my", "name", "is", "jeff")

str_detect(string_vec, "jeff")

str_replace(string_vec, "jeff", "Jeff")
```

* "^i think" begining of the line
* "i think$" end of the line
```{r}
string_vec = c(
  "i think we all rule for participating",
  "i think i have been caught",
  "i think this will be quite fun actually",
  "it will be fun, i think"
  )

str_detect(string_vec, "^i think")
str_detect(string_vec, "i think$")
```
* [Aa]: lower or upper case
```{r}
string_vec = c(
  "Y'all remember Pres. HW Bush?",
  "I saw a green bush",
  "BBQ and Bushwalking at Molonglo Gorge",
  "BUSH -- LIVE IN CONCERT!!"
  )
str_detect(string_vec,"bush")
str_detect(string_vec,"Bush")
str_detect(string_vec,"[Bb]ush")
```
* [0-9][a-zA-Z]: number first followed immediately by letter 
```{r}
string_vec = c(
  '7th inning stretch',
  '1st half soon to begin. Texas won the toss.',
  'she is 5 feet 4 inches tall',
  '3AM - cant sleep :('
  )

str_detect(string_vec, "^[0-9][a-zA-Z]")

```
* "."; match with literally anything
* 7.11= 7x11 (x can be anything)
* to detect exact 7.11, we have to put "7\\.11"
```{r}
string_vec = c(
  'Its 7:11 in the evening',
  'want to go to 7-11?',
  'my flight is AA711',
  'NetBios: scanning ip 203.167.114.66'
  )

str_detect(string_vec, "7.11")
str_detect(string_vec, "7\\.11")
```
* detect open bracket
```{r}
string_vec = c(
  'The CI is [2, 5]',
  ':-]',
  ':-[',
  'I found the answer on pages [6-7]'
  )

str_detect(string_vec, "\\[")


```

## Factors

* we can see which one is reference (assumed as "1")
```{r}
vec_sex = factor(c("male", "male", "female", "female"))
vec_sex

as.numeric(vec_sex)
```

what happens if I relevel...(switch male into reference)

```{r}
vec_sex = fct_relevel(vec_sex,"male")
vec_sex

as.numeric(vec_sex)

````

## NSDUH




